Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-11 paper/structureScene.tex
clean table II
add label in kc eq.
clean some comments

The similarity between two centroids $c_i$ and $c_j$ is computed using a radial basis function (RBF) kernel $K^c$ combined with the local scaling method proposed in \cite{selfTuneManor2004}:
\begin{equation}
K^c_{ij} = exp\left( - \dfrac{\Vert c_i - c_j \Vert^2}{\Vert c_i - c_N \Vert \Vert c_j - c_N \Vert} \right) 
\end{equation}

@@

Lastly, we see that while \emph{ob-c} and \emph{ob-w} perform equivalently for the MFCCs, \emph{ob-c} seems to be able to better characterize the classes than \emph{ob-w} for scattering coefficients. This last observation suggests that weighted a centroid according to the number of frames belonging to it may prove to be a limited solution. Indeed, nothing a priori indicates that the discriminant information between two scenes lays within the majority of their frames. On the contrary, two similar environments  \gl{find examples} may shared a lot of similar sound sources \gl{reformulate}.

@@

\begin{table}
\begin{center}
\begin{tabular}{llll}
              MFCCs &  scattering & log-scattering  \\
             \hline
ei (linear)  & 54 (20)       & 62 (6)  & 66 (11)     \\
ei (RBF)     & 47 (16)       & 56 (7)  & 63 (6)    \\
li (linear)  & 60  (9)       & 70 (8)  & 75 (5)   \\
li (RBF)     & 68 (10)       & 73 (8)  & 78 (6)   \\
\end{tabular}
\caption{FYW: best results for object-based approach with majority vote (on the centroids / on the centroids + on the frames) is circa 75\%}
\end{center}
\end{table}

>>>>

The similarity between two centroids $c_i$ and $c_j$ is computed using a radial basis function (RBF) kernel $K^c$ combined with the local scaling method proposed in \cite{selfTuneManor2004}:
\begin{equation}
\label{eq:kc}
K^c_{ij} = exp\left( - \dfrac{\Vert c_i - c_j \Vert^2}{\Vert c_i - c_N \Vert \Vert c_j - c_N \Vert} \right) 
\end{equation}

@@

Lastly, we see that while \emph{ob-c} and \emph{ob-w} perform equivalently for the MFCCs, \emph{ob-c} seems to be able to better characterize the classes than \emph{ob-w} for scattering coefficients. This last observation suggests that weighted a centroid according to the number of frames belonging to it may prove to be a limited solution. Indeed, nothing a priori indicates that the discriminant information between two scenes lays within the majority of their frames. On the contrary, two similar environments may shared a lot of similar sound sources.

@@

\begin{table}
\begin{center}
\begin{tabular}{llll}
             & MFCCs         & scattering & log-scattering  \\
             \hline
ei (linear)  & 54 (20)       & 62 (6)  & 66 (11)     \\
ei (RBF)     & 47 (16)       & 56 (7)  & 63 (6)    \\
li (linear)  & 60  (9)       & 70 (8)  & 75 (5)   \\
li (RBF)     & 68 (10)       & 73 (8)  & 78 (6)   \\
\end{tabular}
\caption{Accuracies for the best settings}
\end{center}
\end{table}
